Bird beak's elaboration and exploration: data preparation

### 2022-08-29 Analysis/01-Data_preparation.Rmd
removed formspace

```{r}
## Reading the different trait spaces
shapespace <- readRDS("../Data/Raw/Beak_data/2020_08_07_MMB_MORPHO_SHAPESPACE_FULL.rds")
shapespace <- shapespace$PCscores
formspace <- readRDS("../Data/Raw/Beak_data/2020_08_07_MMB_MORPHO_FORMSPACE_FULL.rds")
formspace <- formspace$PCscores
```

```{r, echo = FALSE, fig.height = 16, fig.width = 8}
par(mfrow = c(2,1))
plot.dispRity(shapespace, type = "preview", pch = 21, main = "Shape space")
plot.dispRity(formspace, type = "preview", pch = 21, main = "Form space")
```

>>>>

```{r}
## Reading the different trait spaces
shapespace <- readRDS("../Data/Raw/Beak_data/2020_08_07_MMB_MORPHO_SHAPESPACE_FULL.rds")
shapespace <- shapespace$PCscores
```

```{r, echo = FALSE, fig.height = 16, fig.width = 8}
plot.dispRity(shapespace, type = "preview", pch = 21, main = "Shape space")
```
